\cvsection{Projects \& Research}
\begin{cventries}
%  \cventry
% {\url{www.redditgiftsmap.com}}
%    {redditgifts map}
%    {}
%    {}
%    {
%      \begin{cvitems}
%        redditgifts map is a web application that uses Google's Map API to generate a visual representation of all giftees a redditgifts user has sent gifts to. After creating his or her map, the user can generate both private and share links to refer to it later.
%      \end{cvitems}
%    }
%\cventry
%     {\href{http://pythonpet.com}{pythonpet.com}}
%    {Python Pet}
%    {}
%    {Present}
%    {
%         A Python-powered pet for your command line. Currently in development. 
%    }
%
%\cventry
%     {\href{http://redditgiftsmap.com}{redditgiftsmap.com}}
%    {RedditGifts Map}
%    {}
%    {2014-2016}
%    {
%         This web application uses Google's Map API to generate, save, and edit a visual representation of all giftees of a RedditGifts user. 
%    }
\cventry
     {\href{https://dl.acm.org/doi/10.1145/3408877.3439529}{Link to workshop abstract}}
    {Purposeful Plans for Computer Science Diversity, Equity, and Inclusion}
    {}
    {2021}
    {During this ACM SIGCSE workshop, participants were supported through discussions that focus on specific areas of diversity, equity, and inclusion. Participants left the session with a purpseful plan inspired by new allies and frameworks from the Microsoft Philanthropies TEALS Program to address these issues within their own classrooms.
    }

\cventry
     {\href{https://dl.acm.org/doi/10.1145/3408877.3439559}{Link to presentation abstract}}
    {TEALS's Plans for Addressing Social Justice in Computer Science Education: Creating Inclusive CS Communities}
    {}
    {2021}
    {This ACM SIGCSE lightning talk covered Microsoft Philanthropies TEALS Program's efforts in mititgating the disparity of access and participation of Black and Africian American students in high school computer science classes.
    }

\cventry
     {\href{https://www.semanticscholar.org/paper/Tutorial-of-Twisted-Edwards-Curves-in-Elliptic-Barnard/8eb88f622c8648aa40c2b60171da9d46c2414d5f}{Link to paper}}
    {Twisted Edwards Curves in Elliptic Curve Cryptography}
    {}
    {2015}
    {
         This tutorial introduces Twisted Edwards Curves and relates them to Edwards Curves and Montgomery Curves. It covers projective and other coordinate systems for Twisted Edwards Curves and discusses their application within the Edwards-Curve Digital Signature Algorithm.
    }

  \cventry
     {\href{https://emilie.codes/projects/ca/}{emilie.codes/projects/ca/}}
    {Cellular Automata Encryption Generator}
    {}
    {2013}
    {
         This cellular automata encryption generator allows users to learn about CA encryption techniques in a visual manner. It allows the user to input any CA rule (mod 256) and set output preferences.
    }
\cventry
     {\href{http://pconrad.github.io/AwesomePrelims/}{pconrad.github.io/AwesomePrelims/}}
    {Awesome Library}
    {}
    {2013}
    {
         The idea of this discrete math library is to allow students to self-study various problems related to discrete math, such as set operations and relation classification. I created a 64-bit JavaScript number library which was used to automate question generation.
    }

\cventry{}{}{}{}{More projects can be found on my \underline{\href{https://github.com/emiliebarnard}{GitHub page}}.}

\end{cventries}